Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-18 writeup/gz_hubble_data.tex
Adding references for comparison HST catalogs

For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{hau07}. We selected all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).

@@

\subsection{Effect of changing depth (GOODS, Stripe 82)}

@@

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item GEMS morphologies?
    \item AEGIS morphologies?
    \item GOODS N/S morphologies?
    \item expert visual inspection?
\end{itemize}

>>>>

For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{bar12}. We selected all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).

@@

%\subsection{Effect of changing depth (GOODS, Stripe 82)}

@@

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item GEMS morphologies \citep{hau07}
    \item AEGIS morphologies \citep{lot08}
    \item GOODS N/S morphologies \citep{bun05}
\end{itemize}
